---
title: "Mass/Count Superordinate -- Semantic Inferences from Syntax"
output: html_document
date: "2023-05-11"
---

```{r setup, echo = FALSE, include = FALSE}
library("papaja")
library("knitr") # for knitting things
library("tidyverse") # for all things tidyverse
library("car")
library("lme4")
library("patchwork")
library("effsize")
library("purrr")
library('ggplot2')
library('car')
library('brms')
library('emmeans')
library('easystats')

# these options here change the formatting of how comments are rendered
opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")

#options(mc.cores = parallel::detectCores())

# set the default ggplot theme 
#theme_set(theme_classic())

```

```{r loading data, warning=FALSE, include=F}
df.demog <- read.csv("../data/PROCESSED_DATA/demog.csv")
df.response <- read.csv("../data/PROCESSED_DATA/response.csv")
```

## Demographics Stats

```{r summarize ppt}
df.demog %>%
  filter(demog_question == "gender") %>%
  count(demog_response) %>%
  knitr::kable()

df.demog %>% 
  group_by(subject_id, condition) %>%
  summarise(rows = n()) %>%
  select(-rows) %>%
  group_by(condition) %>%
  count(condition) %>%
  knitr::kable()

df.demog %>% 
  filter(demog_question == "age") %>%
  summarise(mean_age = mean(as.numeric(demog_response)), 
            sd_age = sd(as.numeric(demog_response))) %>%
  knitr::kable()
```

## Results 
No difference between the mass and count syntax conditions (concurrent function dummy coded as 1).
```{r}
t.test(df.response %>% 
         filter(condition == "mass") %>% 
         group_by(subject_id) %>%
         summarise(mean_prop_concurrent_func = mean(selected_concurrent_func, na.rm = T)) %>% 
         pull(mean_prop_concurrent_func),
         mu = 0.5, alternative = "two.sided")

t.test(df.response %>% 
         filter(condition == "count") %>% 
         group_by(subject_id) %>%
         summarise(mean_prop_concurrent_func = mean(selected_concurrent_func, na.rm = T)) %>% 
         pull(mean_prop_concurrent_func),
         mu = 0.5, alternative = "two.sided")
```

```{r}
ggplot(data = df.response, 
       mapping = aes(x = condition, y = selected_concurrent_func, color = condition)) + 
  geom_jitter(aes(group = subject_id), 
              height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none") + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  ylab("Selected concurrent function (by trial)")

ggplot(data = df.response %>%
         group_by(subject_id, condition) %>%
         summarise(mean_concurrent_func = mean(selected_concurrent_func, na.rm = TRUE)),
       mapping = aes(x = condition, y = mean_concurrent_func)) + 
  geom_violin(aes(fill = condition)) +
  geom_jitter(height = 0, 
              alpha = 0.3) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange") +
  theme(legend.position = "none") + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  ylab("Proportion Concurrent Function Selection") + 
  xlab("Syntactic Condition")
```


No differences between mass/count conditions even when grouped by stimuli category (by complexity, function, or complexity x function).
```{r}
ggplot(data = df.response,
       mapping = aes(x = category, y = selected_concurrent_func, color = condition)) + 
  geom_jitter(height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange", 
               position = position_dodge(0.7))  + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  scale_x_discrete(labels = c("high C, high F", "high C, low F", "low C, high F", "low C, low F", "medium C, medium F")) + 
  ylab("Prop. Concurrent Function Selection") + 
  xlab("Category") +
  labs(color = "Syntactic Condition")

ggplot(data = df.response,
       mapping = aes(x = category_complexity, y = selected_concurrent_func, color = condition)) + 
  geom_jitter(height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange", 
               position = position_dodge(0.7))  + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  ylab("Mean concurrent function selection (by participant)")

ggplot(data = df.response,
       mapping = aes(x = category_function, y = selected_concurrent_func, color = condition)) + 
  geom_jitter(height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange", 
               position = position_dodge(0.7))  + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7)) + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  ylab("Mean concurrent function selection (by participant)")
```

Checking if the repeated trials prompt people to be more random with their selections (if this was the case, we might see a significant difference in responding between mass/count conditions in the 1st trial, as opposed to the later trials.)
No distinction between conditions in any trial. But participants chose significantly more individual function groups (for both mass/count conditions) in the 1st trial, and were at chance for the other trials. 

```{r}
ggplot(data = df.response,
       mapping = aes(x = trial_index, y = selected_concurrent_func, color = condition)) + 
  geom_jitter(height = 0, 
              alpha = 0.5) +  
  stat_summary(fun.data = "mean_cl_boot", 
               geom = "pointrange", 
               position = position_dodge(0.7))  + 
  geom_hline(yintercept = 0.5, linetype = "dashed") + 
  ylab("Prop. Concurrent Function Selection") + 
  xlab("Trial #") +
  labs(color = "Syntactic Condition")

fit.trial_ind <- glmer(selected_concurrent_func ~ condition * trial_index + (1|subject_id) + (1|category), 
                       data = df.response %>% 
                         mutate(trial_index = as.factor(trial_index)),
                       family="binomial")
summary(fit.trial_ind)
Anova(fit.trial_ind, type = 3)

fit.trial_ind %>% 
  emmeans(specs = pairwise ~ condition + trial_index,
          adjust = "none")
```

```{r}
t.test(df.response %>% 
         filter(trial_index == 1) %>% 
         group_by(subject_id) %>%
         summarise(mean_prop_concurrent_func = mean(selected_concurrent_func, na.rm = T)) %>% 
         pull(mean_prop_concurrent_func),
         mu = 0.5, alternative = "two.sided")

```


Running the regressions show no effect for any predictors. 

```{r}
fit.base <- glmer(selected_concurrent_func ~ 1 + (1|subject_id) + (1|category), data = df.response, family="binomial")
summary(fit.base)
Anova(fit.base, type = 3)

fit.cond <- glmer(selected_concurrent_func ~ condition + (1|subject_id) + (1|category), data = df.response, family="binomial")
summary(fit.cond)
Anova(fit.cond, type = 3)

anova(fit.base, fit.cond)
```

```{r bayes}
fit.brm_bf1 = brm(formula = selected_concurrent_func ~ 1 + (1|subject_id) + (1|category),
                        data = df.response,
                        save_pars = save_pars(all = T),
                        file = "cache/brm_bf1")

r.fit.brm_bf1 <- report(fit.brm_bf1, verbose = FALSE)

fit.brm_bf2 = brm(formula = selected_concurrent_func ~ condition + (1|subject_id) + (1|category),
                        data = df.response,
                        save_pars = save_pars(all = T),
                        file = "cache/brm_bf2")

r.fit.brm_bf2 <- report(fit.brm_bf2, verbose = FALSE)

bayes_factor(fit.brm_bf2, fit.brm_bf1)
```

```{r}

fit.category <- glmer(selected_concurrent_func ~ condition + category + (1|subject_id), data = df.response, family="binomial")
summary(fit.category)
Anova(fit.category, type = 3)

fit.category_complexity <- glmer(selected_concurrent_func ~ condition + category_complexity + (1|subject_id), data = df.response, family="binomial")
summary(fit.category_complexity)
Anova(fit.category_complexity, type = 3)

fit.category_function <- glmer(selected_concurrent_func ~ condition + category_function + (1|subject_id), data = df.response, family="binomial")
summary(fit.category_function)
Anova(fit.category_function, type = 3)

fit.category_int <- glmer(selected_concurrent_func ~ condition + category_function * category_complexity + (1|subject_id), data = df.response, family="binomial")
summary(fit.category_int)
Anova(fit.category_int, type = 3)
```


